%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------- ELEKTROBIT -----------------------------

\cventry
{Linux Architecte } % Job title
{ELEKTROBIT} % Organization
{Carrières-sur-Seine , France} % Location
{Sep. 2018 - PRESENT} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Arhitecture and support for EB-Linux : an Automotive Linux version of EB , basd on Yocto Open-embedded tools}
\item {This linux is for auto and schould manage virtual containers to run app and shall be aso managed on hypervised environnement by a L4 (Fiasco) Microkernel ..}
\item {Also Responsible for Continous Integration Team: plan, support and follow activity }
\item {CI also include managing testing of the EBLinux using Robot Framewirk and LTP tests ..  }
\item { \textbf{Environment :} Linux,Yocto, Renesas ,L4 Microkernel, CI, Jenkins, RobotFramework}
\end{cvitems}
}


%------------------- EXPWAY -----------------------------

\cventry
{Linux/Android Development Engineer } % Job title
{EXPWAY} % Organization
{PARIS , France} % Location
{Jan. 2018 - Jui. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development of Solution for Public Gateway EMBMS Live Services WIFI multicast}
\item {LTE eMBMS (evolved Multimedia Broadcast Multicast Service) are used to drive live multicast service to end userphones.}
\item { An LTE  Outdoor unit is connected to a Gateway, the soft to be developed will be deployed on PG to activate dash live services and forward multicast packet to WIFI.}
\item {based on Expway Libarary a service will be developped and installed as daemon onBroadcom based public Gateway}
\item { \textbf{Environment :} Modem AT-Command, Broadcom ,Gateway, WIFI, Multicast, dash, EXPWAY Middleware , redmine , C, C++, Android}
\end{cvitems}
}


%------------------- SFR -----------------------------

\cventry
{Software DRM/HDCP Engineer } % Job title
{SFR-Numericable} % Organization
{Saint-Denis , France} % Location
{Feb. 2016 - Dec. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Integration of Netflix nrd 4.3 within new 4K STB .}
\item {Concept and develop a library HDCPmanager that provides interface to manage hdcp link in 1.X and 2.x protocole versions.}
\item {Concept and develop a library DrmManager that provides interfaces to manager Playready 2.5 and eventually Widevine for SFR new Box used for VOD playing }
\item {Concept and develop a library that will install provisioning Data on STB : On factory for SFR new Box ( data : Nagra, HDCP, DRM and SFR keys )}
\item {Integration of STMicroelectronics PlayReady SDK in SFR Set Top Boxes products}
\item {Developing a library interface of STM PlayReady SDK , to be used by SFR Middleware on Set Top Box .}
\item { \textbf{Environment :} STB, STM, Broadcom , Middleware WYPLAY, MW SFR , C, C++, PlayReady 1.2/2.5,TEE, Gentoo, mercurial, Git}
\item { \textbf{References :} Sbastien Keller(SFR), François Delavaud , Anouar Chelbia (SFR), Vishal Sharma ( Netflix)}
\end{cvitems}
}


\cventry
{Netflix integration } % Job title
{}{}
{Aug. 2014 - Jan.2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Integration of Netflix Partner Client Code in Middleware code on Set Top Box Based on 7105 Chip of STM.}
\item {Porting some parts of Netflix client code (audio and video driver  and some Direct FB code ) to work on 7105 based Set Top Box}
\item {Realization of automatic Netflix tests and certification }
\item {Monitoring with Netflix partner via weekly conferences calls between team in US and France and daily coordination integration}
\item { \textbf{Environment :}  STM, MW SFR , C, C++, PlayReady 1.2, DirectFb ,TEE, Gentoo, mercurial, Git}
\item { \textbf{References :} François Delavaud , Anouar Chelbia (SFR), Vishal Sharma ( Netflix)}
\end{cvitems}
}
%---------------- Bouygues --------------------------------    

\cventry
{Software integration \& developping Engineer} % Job title
{Bouygues télécom} % Organization
{Vélizy-villacoublay , France} % Location
{Feb. 2014 - Jun. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development of software module that use a cloud client ( based on PogoPug Fuse solution); So the user could connect , mount  and use his pogo cloud files on her STB}
\item {Development and integration of Media Center new features on Middleware.}
\item { \textbf{Environment :} STB, Middleware Sagem ,Product Bouygues Sensation Box ,  C, C++, Linux, UPNP, DLNA, POGOCLOUD Cloud, Fuse File system,  PacketVideo }
\item { \textbf{References :} Sandrine Figard (Bouygues telecom), Majed Jabri (Bouygues telecom) }
\end{cvitems}
}

\cventry
{Architecte STB for PVR Sharing Service} % Job title
{}{}
{Jun. 2013  - Jan. 2014}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Writing of SSA  (Software Specification Architecture) of service STB PVR sharing (PVR: Personnel Video Recording)  : secured solution based on Protocol HLS  to play STB recorded movies on LAN and WAN devices ; records will be transcoded , segmented , encrypted and served to clients).}
\item {Writing of STS (Software tests Specifications) of PVR Sharing service on STB part of Service.  }
\item { \textbf{Environment :} STB, Middleware Sagem, LibPlatinum, C, C++, Linux, UPNP, HTTP, HTTPS,SSL }
\item { \textbf{References :}  Nicolas Gaude (Bouygues telecom), Jabri Majed(Bouygues telecom) }
\end{cvitems}
}

\cventry
{Software Enginner} % Job title
{}{}
{Sep. 2011 - May. 2013}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Develop Web Services STB Export module that will export multiple STB features (Remote Control, Pairing, PVR, EPG ..) via HTTP Rest and UPNP. }
\item {Develop STB DMR : module proposing DLNA DMR service UPNP  and HTTP Rest. }
\item {Develop MediaPlayer : module STB, for mixed playlist media managements}
\item {Develop Receiver Expo STB : module that serves as a asynchronous full duplex communication library between the Middleware and Web Services Export Binary}
\item {Develop PfsProxy : module on multiple platforms (STB, Android and IOS) of for connection and communication with Bouygues platforms (EPG, PVR, OAuth, Smartvision .. ) with automatic authentication tokens management.}
\item {Develop DMC : module on multiple platforms (STB, Android and IOS)  it’s a UPnP control point }
\item {Development of a Native Middleware on Android (NDK / C / C ++ / JNI / JAVA and JAVASCRIPT) composed from  DMC, DMS and PFSPROXY :
JNI , JAVA and JavaScript Layers for each library ..}
\item { \textbf{Environment :}  Middleware Sagem, STB,   C, C++, Java, JNI, JavaScript, Android, Linux, UPNP,DLNA, SOAP, REST,  LibPlatinum...}
\item { \textbf{References :}  Nicolas Gaude ( Bouygues telecom ), Jabri Majed( Bouygues telecom ), Pascal Souveaux( Bouygues telecom ), Joël Motoumassy ( Bouygues telecom )}
\end{cvitems}
}

%--------------------- NDS ---------------------------

\cventry
{Consulting Engineer} % Job title
{NDS-CISCO} % Organization
{Issy les Moulineaux, France} % Location
{March 2010 - Aug. 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Development and integration of a module within Middleware STB ; it’s a MediaCenter module that allow the sharing and control of medias over networks via Upnp/Dlna Protocol.}
\item {DMS (Digital Media Server) solution is Twonky from PacketVideo company }
\item {Development of a module in C for control and management of the Twonky server via RPC and for sharing FTA PVR and media content from USB drives connected to the STB}
\item {Development and JAVA JNI  layer of the module to be exploited later by the UI in JAVA}
\item { \textbf{Environment :}Middleware MHP de NDS-CISCO, languages C and JAVA, Shell, Makefiles, UPNP, PV Twonky API, PV Twonky Server. }
\item { \textbf{References :} Hassen Taleb (NDS-CISCO) , Eric Delaunay (NDS-CISCO) }
\end{cvitems} 
}

%---------------------- Sagem Defense --------------------------

\cventry
{Software Engineer Development} % Job title
{Sagem Défense} % Organization
{Massy-Palaiseau, France} % Location
{Dec. 2009 - Feb. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {TMA : Third Maintenance Application of Network Server System on aircraft Airbus A380}
\item { \textbf{Environment :} C, C++, Java, Perl, Python, SGBD MYSQL, Linux .. }
\end{cvitems}
}

%----------------------- Eurogiciel -------------------------

\cventry
{Software Engineer} % Job title
{Eurogiciel} % Organization
{Tunis, Tunisia} % Location
{May. 2009 - Nov. 2009} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Design and implementation of an application that manage a Switch via i2C in the NSS (Network System Server) for the Airbus A380}
\item {The PSM, interfaces with LDAP, VPN, an I2C interface to control the Switch and a  Flight switches.}
\item {Test are automatized in virtual environment using Perl scripting and shared memory C programs . }
\item { \textbf{Environment :} C, tested and integrated under Linux FreeBsd 5.3. , perl ..}
\end{cvitems}
}

%---------------------- STMicro --------------------------

\cventry
{Set Top Box Low Layer development Engineer,} % Job title
{STMicroelectronics} % Organization
{Tunis, Tunisia } % Location
{Out. 2007 – Apr. 2009} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Engineer in STAPI (ST-API)  team : responsible for development, maintenance and support for VOUT (Video Output Stage) and HDMI (High Definition Multimedia Interface) drivers for STM socks.}
\item {Bug fixing  and support  for various clients. }
\item {Porting of drivers code on new chips and update documentation of drivers for new socks }
\item { \textbf{Environment :} C, OS21, STLinux, Clear Case, socks: ST7100, ST7109, ST7200 et ST7105. }
\end{cvitems}
}

%------------------------------------------------
\clearpage
\end{cventries}